Hierarchical Controller Architecture in Software Defined Networks

### 2013-12-16 paper/paper.tex
minor changes

\subsection{Optimization}
Let's say there are \emph{n} controller domains. Each controller domain, $i$ maintains a vector timestamp $T_{i}[1...n]$, where $T_{i}[j]$ contains the latest revision number of domain $j$'s network state (link utilizations), seen by domain $i$. Whenever links utilization is revised for links in domain $i$, the controller increments it's own revision number $T_{i}[i]$ in the timestamp. Timestamps are sent along with network state to other controllers for replication. During replication, a controller revises it's timestamp with the incoming timestamp by taking maximum for each entry between the two timestamps. This is a general technique for any replicated system. Each router is updated with the latest timestamp of it's parent controller.

When a route is being set up, the controller prints it's timestamp on packet header along with the route. When a router in a domain $i$ receives a flow with timestamp $T_{j}$ , it checks for any index k such that $T_{j} [k] < T_{i} [k]$. For all such index's, it recalculate the part of the route which belongs to domain $k$ using it's own network state. This is because these parts of existing path were calculated on stale network state.

>>>>

\subsection{Optimization}
Let's say there are \emph{n} controller domains. Each controller domain, $i$ maintains a vector timestamp $T_{i}[1...n]$, where $T_{i}[j]$ contains the latest revision number of domain $j$'s network state (link utilizations), seen by domain $i$. Whenever links utilization is revised for links in domain $i$, the controller increments its own revision number $T_{i}[i]$ in the timestamp. Timestamps are sent along with the network state to other controllers for replication. During replication, a controller revises its timestamp with the incoming timestamp by taking maximum for each entry between the two timestamps. This is a general technique for any replicated system. Each router is updated with the latest timestamp of its parent controller.

When a route is being set up, the controller prints its timestamp on packet header along with the route. When a router in a domain $i$ receives a flow with timestamp $T_{j}$ , it checks for any index $k$ such that $T_{j} [k] < T_{i} [k]$. For all such indices, it recalculates the part of the route which belongs to domain $k$ using its own network state. This is because these parts of the existing path were calculated on a stale network state.
